Blocking-resistant communication\\through domain fronting

### 2014-07-30 docs/meek.tex
Replace "meek" with "\meek"
In case we want to change the font or style.

% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
%         811         783         151        1263
% 0.012312668 0.007811963 0.007031241 0.006569205
\begin{table}[ht]
\normalsize
\centering
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 2.9\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{The most common TCP payload lengths.}
\label{tab:datalen}
\end{table}

>>>>

% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405263438 0.376721457 0.071558122 0.019904635 0.018484229 0.014867466
%         811         783         151        1263
% 0.012312158 0.007811639 0.007030949 0.006568932
\begin{table}[ht]
\normalsize
\centering
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
0 bytes & 37.7\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.8\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 3.0\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{The most common TCP payload lengths.}
\label{tab:datalen}
\end{table}
